COG-ED Manuscript

### 2022-02-14 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
      - Visualization
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
abstract: |
  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  One approach to quantify the SVs of levels of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
  Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
  We aim to replicate the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.

@@

@@

A way to quantify the subjective cost of each *n*-back level has been developed by Westbrook, Kester, and Braver [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
First, the participants complete the *n*-back levels to familiarize themselves with the task.
Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for 1-back.
If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if they choose 1-back, it decreases by 0.50\$.
This is repeated five more times, with each adjustment of the 1-back reward being half of the previous step, while the reward for the more difficult level remains fixed at 2\$.
The idea is to estimate the point of subjective equivalence, i.e., the monetary ratio at which both offers are equally preferred [@Westbrook2013].
The subjective value (SV) of each difficulty level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
Westbrook et al. [-@Westbrook2013] <!-- I guess, it is easier to simply write @Westbrook2013 instead of Westbrook et al. [-@Westbrook2013], but this may be sinply a matter of the nature.csl --> used these SVs to investigate inter-individual differences in effort discounting (ED) <!-- perhaps avoid the abbreviation and simoly always write effort discounting -->.
Younger participants showed lower ED, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.

@@

With he present study, we change <!-- in my opinion better: alter --> one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
We therfore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
Figure\ 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
Adding a comparison of 2-back and 3-back allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
Adding three more comparisons of the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
The level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
The level that was not chosen will be set to a fixed value of 2€.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
Each level's SV is calculated as the mean of this level's SVs from all comparisons in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks <!-- perhaps add ref. to the other ms. on this issue? -->, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
Additionally, we will compare the ED behaviour of participants regarding the *n*-back task and an emotion regulation task.
The full results of the latter will be published in a second Registered Report<!-- again: add (interim) ref. -->.
The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.

@@

Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with increasing n-back level.
Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) they do so even after controlling for declining task performance.
Here we added the hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
Each hypothesis is detailed in the Design Table in the Appendix.

@@

  # create new data frames for the specification curve analysis
  # the data frame names are a combination of the letters from each of these categories, indicating how they will be preprocessed:
  #
  # across which dimensions the transformation and outlier exclusion will be done:
  #   (AA) across subjects, across n-back levels
  #   (AW) across subjects, within n-back levels
  #   (WW) within subjects, within n-back levels
  #   (WA) within subjects, across n-back levels
  # RT transformations:
  #   (R) raw/none
  #   (L) log
  #   (I) inverse
  #   (S) square-root
  # RT outlier exclusion:
  #   (N) none
  #   (2) 2 MADs from the median
  #   (5) 2.5 MADs from the median
  #   (3) 3 MADs from the median
  #   (O) 0-100 ms after stimulus onset
  #   (T) 0-200 ms after stimulus onset
  #
  # Example: the data frame "AWL3" has log-transformed RT data with no data points beyond 3 MADs
  # from the median
  #
  # Some combinations are nonsensical, so we will not include them: Raw data sets (__R__) with either no outlier
  # exclusion (___N_) or time-based outlier exclusion (___T_) do not need the different dimensions (A/W), and
  # time-based exclusion is nonsensical for transformed data sets.

>>>>

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
      - Visualization
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    <!-- to be discussed -->
    role: 
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
      - Visualization
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
abstract: |
  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  One approach to quantify the SVs of levels of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
  Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
  We aim to replicate the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.

@@

<!-- wouldn't it be more intellegible if the following code chunks are placed where the respective analyses are introducecommented on? -->

@@

A way to quantify the subjective cost of each *n*-back level has been developed by Westbrook, Kester, and Braver [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
First, the participants complete the *n*-back levels to familiarize themselves with the task.
Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for 1-back.
If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if they choose 1-back, it decreases by 0.50\$.
This is repeated five more times, with each adjustment of the 1-back reward being half of the previous step, while the reward for the more difficult level remains fixed at 2\$.
The idea is to estimate the point of subjective equivalence, i.e., the monetary ratio at which both offers are equally preferred [@Westbrook2013].
The subjective value (SV) of each difficulty level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
Westbrook et al. [-@Westbrook2013] <!-- I guess, it is easier to simply write @Westbrook2013 instead of Westbrook et al. [-@Westbrook2013], but this may be a matter arising because of the use of the nature.csl --> used these SVs to investigate inter-individual differences in effort discounting (ED) <!-- perhaps avoid the abbreviation and simply always write effort discounting, we had some issues recently when using abbreviations in a manuscript, but we were using a lot of them, so it may be ok to use one or two here -->.
Younger participants showed lower ED, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.

@@

With he present study, we change <!-- in my opinion better: alter --> one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
We therfore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
Figure\ 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
Adding a comparison of 2-back and 3-back allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
Adding three more comparisons of the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
The level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
The level that was not chosen will be set to a fixed value of 2€.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
Each level's SV is calculated as the mean of this level's SVs from all comparisons in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks <!-- perhaps add ref. to the other ms. on this issue? -->, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED). <!-- not sure whether you should call it like this; while it reflects the so-called "Entstehungszusammenhang", it does not necessarily reflect the so-called "Begründungszusammenhang", i.e., the proposed approach goes beyond emotion regulation, but applies to  
In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
Additionally, we will compare the ED behaviour of participants regarding the *n*-back task and an emotion regulation task.
The full results of the latter will be published in a second Registered Report<!-- again: add (interim) ref. -->.
The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.

@@

Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing *n*-back level, (1b) reaction time increases with increasing *n*-back level, and (1c) perceived task load increases with increasing *n*-back level.
Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
Here we added <!-- why this 'here we added'? --> the hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores,
and regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
Each hypothesis is detailed in the Design Table in the Appendix.

@@

  # create new data frames for the specification curve analysis <!-- specification curve analysis has not been mentioned in the ms. so far -->
  # the data frame names are a combination of the letters from each of these categories, indicating how they will be preprocessed:
  #
  # across which dimensions the transformation and outlier exclusion will be done:
  #   (AA) across subjects, across n-back levels
  #   (AW) across subjects, within n-back levels
  #   (WW) within subjects, within n-back levels
  #   (WA) within subjects, across n-back levels
  # RT transformations:
  #   (R) raw/none
  #   (L) log
  #   (I) inverse
  #   (S) square-root
  # RT outlier exclusion:
  #   (N) none
  #   (2) 2 MADs from the median
  #   (5) 2.5 MADs from the median
  #   (3) 3 MADs from the median
  #   (O) 0-100 ms after stimulus onset
  #   (T) 0-200 ms after stimulus onset
  #
  # Example: the data frame "AWL3" has log-transformed RT data with no data points beyond 3 MADs
  # from the median
  #
  # Some combinations are nonsensical, so we will not include them: Raw data sets (__R__) with either no outlier
  # exclusion (___N_) or time-based outlier exclusion (___T_) do not need the different dimensions (A/W), and
  # time-based exclusion is nonsensical for transformed data sets.
